2024 US Presidential Election Model

### 2024-10-19 paper/paper.qmd
rendering pdf

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

#modelsummary::modelsummary(
  #list(
    #"First model" = first_model
 # ),
 # statistic = "mad",
 # fmt = 2
#)
```

@@

#pp_check(first_model) +
  #theme_classic() +
  #theme(legend.position = "bottom")

#posterior_vs_prior(first_model) +
 # theme_minimal() +
  #scale_color_brewer(palette = "Set1") +
 # theme(legend.position = "bottom") +
  #coord_flip()
```

@@

#plot(first_model, "trace")

#plot(first_model, "rhat")
```
